`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-06-16 inst/manuscript/manuscript.rmd
Proper reflection od "generation_of_algorithm = 2" as the default;

Figure 2A emphasizes reproducibility between independent experiments
("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
reproducibility analysis in favor of a potentially more reliable result and
following more closely the analysis in Figure 4C/D by
following more closely the analysis in Figure 4C--F by
@ploier_perturbed_submitted, a single fit may be performed for the combined data
from all experiments as follows, resulting in Figure 2B:

@@

```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats(
  "inputTable.txt",
  generation_of_algorithm = 2,
  split_by_experiment = FALSE)
```

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- scramblase_assay_stats(
    x, generation_of_algorithm = 2, split_by_experiment = FALSE) %>%
  mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
  set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
ppr_results_names <- ppr_results %>%
  extract2("Experimental Series") %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results %>%
  extract2("Fit Constant ($\\times 10^4$)") %>%
  round(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant ($\\times 10^4$)`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    time_max_sec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 2)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 2,
    split_by_experiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 2, 
    split_by_experiment = FALSE)
}

>>>>

Figure 2A emphasizes reproducibility between independent experiments
("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
reproducibility analysis in favor of a potentially more reliable result and
following more closely the analysis in Figure 4C--F by
@ploier_perturbed_submitted, a single fit may be performed for the combined data
from all experiments as follows, resulting in Figure 2B:

@@

```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats(
  "inputTable.txt",
  split_by_experiment = FALSE)
```

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- scramblase_assay_stats(
    x, split_by_experiment = FALSE) %>%
  mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
  set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
ppr_results_names <- ppr_results %>%
  extract2("Experimental Series") %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results %>%
  extract2("Fit Constant ($\\times 10^4$)") %>%
  round(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant ($\\times 10^4$)`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    time_max_sec = 350)
  scramblase_assay_plot(
    x)
  scramblase_assay_plot(
    x,
    split_by_experiment = FALSE)
  scramblase_assay_stats(
    x,
    split_by_experiment = FALSE)
}
